PaperOutline_ACEsCog

### 2022-01-26 PaperOutline_ACEsCog.Rmd
added site covariate
added random effect for ABCD site - results don't change

@@

abcd.data<-merge(abcd.data.almost,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data.almost)))],by="subjectkey")

@@

## Run linear mixed effects models!
```{r}
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance+monitoring,data=abcd.data))

>>>>

# also add in the variable for site ID to use as a covariate
site_info <- readRDS("/Users/ariellekeller/Documents/Kellernet_PrelimAnalysis/DEAP-siteID.rds")
site.baseline<-site_info[site_info$event_name=="baseline_year_1_arm_1",]
colnames(site.baseline)[1]<-"subjectkey"
abcd.data.withFamAndSite <- merge(abcd.data.almost,site.baseline[,c("subjectkey", setdiff(colnames(site.baseline),colnames(abcd.data.almost)))],by="subjectkey")

@@

abcd.data<-merge(abcd.data.withFamAndSite,neglect.data[,c("subjectkey", setdiff(colnames(neglect.data),colnames(abcd.data.withFamAndSite)))],by="subjectkey")

@@

## Run linear mixed effects models!
```{r}
summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+(1|abcd_site)+acceptance+monitoring,data=abcd.data))
